---
title: "Introduction to oneway package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{oneway}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, message=FALSE, warning=FALSE,
  comment = "#>"
)
```

## Introduction

The **oneway* package provides a simple interface for completing a
one-way Analysis of Variance (ANOVA). This is useful when evaluating mean
differences between groups on a quantitative variable.

### Setup and results table

First the model is fit. In this example, we want to know if there is a difference in fuel efficiency based on the number of cylinders in a car engine. The data come from the `mtcars` dataset.

Summary statistics and the ANOVA results are printed.

```{r}
library(oneway)
fit <- oneway(mpg ~ cyl, data = mtcars)
print(fit)
```

These results can be summarized using the `summary` generic function.

```{r}
summary(fit)
```

### Plotting the results

Group differences can be visualized using three types of plot - boxplot, violin plot, and ridges plots.

```{r}
plot(fit, plot="boxplot")
```

```{r}
plot(fit, plot="violin")
```

```{r}
plot(fit, plot="density_ridges")
```

### Test Assumptions

The results assume normality of the outcome variable (mpg) and equal variances on this variable for the three groups. We can test this with the `assumptions` function.

```{r}
assumptions(fit)
```

Here, we can see the the normality assumption is met, but 4 cylinder cars 
have greater variance.

### Post hoc comparisons

The ANOVA test indicates that the groups are different, but not where the differences lie. The `posthoc` function performs pairwise comparisons, controlling for the number of tests performed.

```{r}
posthoc(fit)
```

You can see that all three groups differ, with increased cylinders leading to decreased fuel efficiency.
